SpARC: Sparse Redundant Calibration

### 2016-09-23 paper.tex
newest paper version
added paper

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{equation}
d_{pq} = g_{p}\conj{g}_{q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Conjugation is denoted by $\conj{(*)}$. During an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which have 
to be estimated.

The thermal noise is normally distributed with a mean of zero and a standard deviation that is equal to  
\begin{equation}
\sigma = \frac{\sqrt{2}k_{B}T_{\textrm{sys}}}{A\eta\sqrt{\Delta \nu \tau}}, 
\end{equation}
where $k_B$ is Boltzmann's constant, $T_{\textrm{sys}}$ is equal to the system temperature, $A$ is the effective collecting area of each element in the array, $\eta$ is a dimensionless
efficiency factor, $\Delta \nu$ is the observational bandwidth and $\tau$ is the integration time per visibility. The

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{equation}
d_{pq} = g_{p}\conj{g}_{q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Conjugation is denoted by $\conj{(*)}$. During the course of an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which infact have 
to be estimated.

The thermal noise is normally distributed with a mean of zero and a standard deviation that is equal to  
\begin{equation}
\sigma = \frac{\sqrt{2}k_{B}T_{\textrm{sys}}}{A\eta\sqrt{\Delta \nu \tau}}, 
\end{equation}
where $k_B$ is Boltzmann's constant, $T_{\textrm{sys}}$ is equal to the system temperature, $A$ is the effective collecting area of each element in the array, $\eta$ is a dimensionless
efficiency factor, $\Delta \nu$ is the observational bandwidth and $\tau$ is the integration time per visibility.

Eq can also be restated in vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{eqnarray}
 \bd &=& [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q),\nonumber\\
 \bv &=& [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q),\nonumber\\
 \bn &=& [n_{pq}]  \big \} ~ [pq] = 1\cdots N ~ (p<q).
\end{eqnarray}

\begin{equation}
  \bd = [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q),
\end{equation}
\begin{equation}
  \bv = [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q)
\end{equation}
and
\begin{equation}
  \bn = [n_{pq}]  \big \} ~ [pq] = 1\cdots N ~ (p<q).
\end{equation}

\begin{enumerate}
 \item $\bd$ is the observed visibility vector, i.e. 
 \begin{equation}
  \bd = [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 The vector entry $d_{pq}$ denotes the observed visibility associated with the baseline formed by antenna $p$ and $q$, while $N$ denotes the number or antennas
 in the array. 
 \item $\bg = [g_1,g_2,\cdots,g_N]$ represents the instrumental complex antenna gain vector.
 \item $\bv(\bg)$ denotes the predicted visibility vector, i.e.
 \begin{equation}
  \bv(\bg) = [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 In Eq... $y_{pq}$ denotes the visibility which was created from a skymodel and is associated with antenna $p$ and $q$. [Need to rw this sentence] 
\end{enumerate}

The SNR is defined as 
\begin{equation}
\textrm{SNR} = \frac{<\bv\odot\conj{\bv}>_{t,pq}}{<\bn\odot\conj{\bn}>_{t,pq}}, 
\end{equation}
where $<*>_{t,pq}$ denotes averaging over time and baselines and $\odot$ denotes the Hadamard product.
